---
title       : Insert the chapter title here
description : Insert the chapter description here
attachments :
  slides_link : https://s3.amazonaws.com/assets.datacamp.com/course/teach/slides_example.pdf

--- type:NormalExercise lang:r xp:100 skills:1 key:60677f2f4c
## Intersection 1

Given is a fuction \\(f(x) = ax+b\\), with two pairs of values for \\(a\\) and \\(b\\).

*** =instructions
- Calculate the intersection for $(a_1 = -3, b_1 = -1)$ and $(a_2 = -1, b_2 = -3)$.

*** =hint
- to create a variable use `<-`

*** =pre_exercise_code
```{r}
#nothing for these example
```

*** =sample_code
```{r}
# Create two variables x and y with equals to the solution
# Create a variable x, equal to the solution of x


# Create a variable y, equal to the solution of y

```

*** =solution
```{r}
# Create two variables x and y with equals to the solution
# Create a variable x, equal to the solution of x
x <- 1

# Create a variable y, equal to the solution of y
y <- -4

```

*** =sct
```{r}
# SCT written with testwhat: https://github.com/datacamp/testwhat/wiki

test_function("str", args = "object",
              not_called_msg = "You didn't call `str()`!",
              incorrect_msg = "You didn't call `str(object = ...)` with the correct argument, `object`.")

test_object("good_movies")

test_function("plot", args = "x")
test_function("plot", args = "y")
test_function("plot", args = "col")

test_error()

success_msg("Good work!")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:27e4552b3e
## Intersection 2
 
You see a plot for the give fuction \\(f(x) = ax+b\\.

*** =instructions
- Please insert the intersection point.

*** =hint
- to create a variable use `<-`
- click on the tab plot, you can use a separate window

*** =pre_exercise_code
```{r}
library(ggplot2)

# create values for a plot of two lines
xMin <- -5
xMax <- 5

a1 <- -2
a2 <- 1
b1 <- -1
b2 <- -1

#build dataframe for ggplot
x <- c(xMin:xMax)
y1 <- c(a1*x+b1)
y2 <- a2*x+b2
#use rbind to combine the rows of dataset for (x,y1) and (x,y2)
#indefied by column func (for fuction f1 and f2)
data <- rbind(data.frame(x,func="f1",y=y1),data.frame(x,func="f2",y=y2))

#simple plot of two lines
ggplot(ds$data, aes(x=x, y=y, color=func)) + geom_line() + labs(x = "X", y = "Y")

x.PoI <- (b2-b1)/(a1-a2)
y.PoI <- x.PoI*a1 + b1
```

*** =solution
```{r}
# Create two variables x and y with equals to the solution
# Create a variable x, equal to the solution of x
x <- 0

# Create a variable y, equal to the solution of y
y <- -1

```

*** =sct
```{r}
# SCT written with testwhat: https://github.com/datacamp/testwhat/wiki
test_object("x",
            undefined_msg = "Make sure to define `x`!",
            incorrect_msg = "That is not the correct solution for `x`!")
test_object("y",
            undefined_msg = "Make sure to define `y`!",
            incorrect_msg = "That is not the correct solution for `y`!")
success_msg("Great!")
```