---
title       : Mathtest
description : Example mathemtatics test
attachments :
  slides_link : https://s3.amazonaws.com/assets.datacamp.com/course/teach/slides_example.pdf

--- type:NormalExercise lang:r xp:100 key:60677f2f4c
## Intersection 1

Given is a fuction \\(f(x) = ax+b\\), with two pairs of values for \\(a\\) and \\(b\\). 

*** =instructions

- Calculate the intersection for f_1(x) = -3x-1 and f_2(x) = -1x-3. 


*** =hint
- to create a variable use `<-`

*** =pre_exercise_code
```{r}
#nothing for these example
```

*** =sample_code
```{r}
# Create two variables x and y with equals to the solution
# Create a variable x, equal to the solution of x


# Create a variable y, equal to the solution of y

```

*** =solution
```{r}
# Create two variables x and y with equals to the solution
# Create a variable x, equal to the solution of x
x <- 1

# Create a variable y, equal to the solution of y
y <- -4

```

*** =sct
```{r}
# SCT written with testwhat: https://github.com/datacamp/testwhat/wiki

test_object("x",
            undefined_msg = "Make sure to define `x`!",
            incorrect_msg = "That is not the correct solution for `x`!")
test_object("y",
            undefined_msg = "Make sure to define `y`!",
            incorrect_msg = "That is not the correct solution for `y`!")

test_error()

success_msg("Good work!")
```

--- type:NormalExercise lang:r xp:100 key:27e4552b3e
## Intersection 2
 
You see a plot for the give fuction \\(f(x) = ax+b\\).

*** =instructions
- Please insert the intersection point.

*** =hint
- to create a variable use `<-`
- click on the tab plot, you can use a separate window

*** =pre_exercise_code
```{r}
library(ggplot2)

# create values for a plot of two lines
xMin <- -5
xMax <- 5

a1 <- -2
a2 <- 1
b1 <- -1
b2 <- -1

#build dataframe for ggplot
x <- c(xMin:xMax)
y1 <- c(a1*x+b1)
y2 <- a2*x+b2
#use rbind to combine the rows of dataset for (x,y1) and (x,y2)
#indefied by column func (for fuction f1 and f2)
data <- rbind(data.frame(x,func="f1",y=y1),data.frame(x,func="f2",y=y2))

#simple plot of two lines
ggplot(data, aes(x=x, y=y, color=func)) + geom_line() + labs(x = "X", y = "Y")

x.PoI <- (b2-b1)/(a1-a2)
y.PoI <- x.PoI*a1 + b1
```

*** =sample_code
```{r}
# Create two variables x and y with equals to the solution
# Create a variable x, equal to the solution of x


# Create a variable y, equal to the solution of y

```


*** =solution
```{r}
# Create two variables x and y with equals to the solution
# Create a variable x, equal to the solution of x
x <- 0

# Create a variable y, equal to the solution of y
y <- -1

```

*** =sct
```{r}
# SCT written with testwhat: https://github.com/datacamp/testwhat/wiki
test_object("x",
            undefined_msg = "Make sure to define `x`!",
            incorrect_msg = "That is not the correct solution for `x`!")
test_object("y",
            undefined_msg = "Make sure to define `y`!",
            incorrect_msg = "That is not the correct solution for `y`!")

test_error()

success_msg("Good work!")
```

--- type:NormalExercise lang:r xp:100 key:0a2883353e
## Mean, Median and Variance
 
Given are 5 numbers, 18, 4, 1, -4 and 16.

*** =instructions
- Please calculate the mean, median and variance!
- write it to 3 seperate variables

*** =hint
- try to use the console with commands like `mean()` :-)

*** =sample_code
```{r}
# Mean as variable mean


# Median as variable med


# Variance as variable var


```


*** =solution
```{r}
# Mean as variable mean
mean <- 7

# Median as variable med
med <- 4

# Variance as variable var
var <- 92

```

*** =sct
```{r}
# SCT written with testwhat: https://github.com/datacamp/testwhat/wiki
test_object("mean",
            undefined_msg = "Make sure to define `mean`!",
            incorrect_msg = "That is not the correct solution for `mean`!")
test_object("med",
            undefined_msg = "Make sure to define `med`!",
            incorrect_msg = "That is not the correct solution for `med`!")
test_object("var",
            undefined_msg = "Make sure to define `var`!",
            incorrect_msg = "That is not the correct solution for `var`!")

test_error()

success_msg("Good work!")
```

--- type:MultipleChoiceExercise lang:r xp:50 key:fa84755598
## Fun Question

What is the "Answer to the Ultimate Question of Life, the Universe, and Everything" ?


*** =instructions
- Douglas Adams don't tell us
- 324354335434678
- 42
- ca. 10

*** =hint
Maybe you will find the answer at Wikipedia by looking for "The Hitchhiker's Guide to the Galaxy"

*** =sct
```{r}
# SCT written with testwhat: https://github.com/datacamp/testwhat/wiki

msg_bad <- "No, that is not the correct answer"
msg_success <- "Yes, you are right!"
test_mc(correct = 3, feedback_msgs = c(msg_bad, msg_bad, msg_success, msg_bad))
```


